Computational musicology, ????, Profit

### 2016-07-31 paper.tex
Mild edit.

\begin{abstract}
In this paper I examine the relationship of complexity theory and disjunctive sequences to music, music-generating programs and
literary works. I then apply these ideas by devising a program to generate an infinite `copyright infringement song' that contains
all other songs within it. I adopt literary modes of analysis and presentation, which I motivate by
arguing that music is a cultural and artistic phenomenon rather than a natural one.
\end{abstract}

@@

On a practical level, algorave musicians are already well advanced in finding a solution to the ``problem" of reconciling
computation with creative practice\cite{Algorave}. These performers generate music by writing code in front of a live audience.
They explore the
potential and the limits of programming as a musical instrument. For them, live coding is a challenge of language and expression.
If the praxis of programming and musical performance can be fruitfully combined, then surely literary and scientific theory
might also be brought together.

@@

Using this idea, we can show that composing ``Row, row, row your boat" out of sequences of durations and pitches
is a better description of the piece than the raw notes. \verb|;| indicates a comment in Clojure.

@@

The particularly significant compression in this way of writing ``Row, row, row your boat" is the line \verb|(canon (simple 4))|.
A canon is when an initial melody (often known as the dux) is accompanied by a transformation of itself (often known as the comes).
In ``Row, row, row your boat", the comes is a copy of the dux that is delayed by four beats, a structure known as a simple canon.

>>>>

\begin{abstract}
In this paper I examine the relationship that complexity theory and disjunctive sequences have to music, music-generating programs
and literary works. I then apply these ideas by devising a program to generate an infinite `Copyright Infringement Song' that
contains all other songs within it. I adopt literary modes of analysis and presentation, which I motivate by
arguing that music is a cultural and artistic phenomenon rather than a natural one.
\end{abstract}

@@

On a practical level, algorave musicians are already well advanced in finding a solution to the ``problem" of reconciling
computation with creative practice\cite{Algorave}. These performers generate music by writing code in front of a live audience.
They explore the
potential and the limits of programming as a musical instrument. For them, live coding is a challenge of language and expression.
If the praxis of programming and musical performance can be fruitfully combined, then literary and scientific theory
might also be brought together.

@@

Using this idea, we can show that composing `Row, row, row your boat' out of sequences of durations and pitches
is a better description of the piece than the raw notes. \verb|;| indicates a comment in Clojure.

@@

The particularly significant compression in this way of writing `Row, row, row your boat' is the line \verb|(canon (simple 4))|.
A canon is when an initial melody (often known as the dux) is accompanied by a transformation of itself (often known as the comes).
In `Row, row, row your boat', the comes is a copy of the dux that is delayed by four beats, a structure known as a simple canon.
